TacticToe: Learning to Prove with Tactics

### 2018-02-19 tactictoe_jv.tex
more

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function
that takes a goal (or proof obligation) and returns a list of goals (subgoals 
of the original goal) together
with a validation function.
Calling the validation function on a list of \emph{theorems}, corresponding to 
the list of subgoals, results in a theorem corresponding to the original goal.
For example, if the list of subgoals is empty, then calling the validation 
function on the empty list yields the originally goal sequent as a theorem.
In this way, tactics implement the plumbing of backwards, goal-directed, proof 
construction. 
Because validation functions are only important to check the final proof, we 
omit them during the description of proof search algorithm. We note $t(g)$ 
the lists of goals produced by the application of a tactic $t$ to a goal 
$g$.

@@

Here are the different kind of feature we extract from terms:
\begin{itemize}
\item names of constants, including the logical operators,
\item type constructors present in the types of constants and variables,
\item subterms with all variables replaced by a single place holder $V$,
\item names of the variables.
\end{itemize} 
Goals (respectively theorems) are represented by a couple of a list of 
terms (assumptions) and a term (conclusion). So, we distinguish between
features of the assumptions and features of the conclusion by adding a
different tag to elements of each set. The union of all those 
features are considered the feature of a goal (respectively theorem). From 
that, we can construct features for a list of goals by
from the union of the features of each goal in the list.

@@

\paragraph{Abstraction of Tactic Arguments}
The first step is to abstract arguments of tactics by replacing them by a
place holder, creating a tactic with an unspecified argument.
Suppose we have a recorded tactic $t$. Since $t$ is a \sml code tree, we can
try to abstract any of the
\sml subterms. Let $u$ be a \sml subterm of $t$, and $h$ a placeholder $u$, we
can substitute $u$ by $h$ to create an abstracted tactic.
We note this intermediate tactic $t[h/u]$. By repeating the
process, multiple
arguments may be abstracted in the same tactic. Ultimately, the more
abstractions are performed the more general a tactic is, as many tactics
become instances of the same abstracted tactic. As a consequence, it becomes 
harder and harder to predict suitable arguments. In our experiments, we create 
one abstraction $\hat{t}$ for each tactic $t$ by abstracting all subterms of 
type theorem list in $t$.

>>>>

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function
that takes a goal (or proof obligation) and returns a list of goals (subgoals 
of the original goal) together
with a validation function.
Calling the validation function on a list of \emph{theorems}, corresponding to 
the list of subgoals, results in a theorem corresponding to the original goal.
For example, if the list of subgoals is empty, then calling the validation 
function on the empty list yields the originally goal sequent as a theorem.
In this way, tactics implement the plumbing of backwards, goal-directed, proof 
construction. 
Because validation functions are only important to check the final proof, we 
omit them during the description of proof search algorithm. We denote $t(g)$ 
the lists of goals produced by the application of a tactic $t$ to a goal 
$g$.

@@

Here are the different kind of feature we extract from terms:
\begin{itemize}
\item names of constants, including the logical operators,
\item type constructors present in the types of constants and variables,
\item subterms with all variables replaced by a single placeholder $V$,
\item names of the variables.
\end{itemize} 
Goals (respectively theorems) are represented by a couple of a list of 
terms (assumptions) and a term (conclusion). So, we distinguish between
features of the assumptions and features of the conclusion by adding a
different tag to elements of each set. The union of all those 
features are considered the feature of a goal (respectively theorem). From 
that, we can construct features for a list of goals by
from the union of the features of each goal in the list.

@@

\paragraph{Abstraction of Tactic Arguments}
The first step is to abstract arguments of tactics by replacing them by a
placeholder, creating a tactic with an unspecified argument.
Suppose we have a recorded tactic $t$. Since $t$ is a \sml code tree, we can
try to abstract any of the
\sml subterms. Let $u$ be a \sml subterm of $t$, and $h$ a placeholder in $u$, we
can substitute $u$ by $h$ to create an abstracted tactic.
We denote this intermediate tactic $t[h/u]$. By repeating the
process, multiple
arguments may be abstracted in the same tactic. Ultimately, the more
abstractions are performed the more general a tactic is, as many tactics
become instances of the same abstracted tactic. As a consequence, it becomes 
harder and harder to predict suitable arguments. In our experiments, we create 
one abstraction $\hat{t}$ for each tactic $t$ by abstracting all subterms of 
type theorem list in $t$.
